*DCVtestkit*: a R package for linearity assessment and visualisation of multiple curves

### 2022-11-09 Manuscript/manuscript.qmd
Make the figure size bigger.

::: {#fig-overview layout="[[50,-50], [60,-40]]"}
![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}

![Interactive Trellis Plots](images/README-TrellisOutput.png){#fig-visualisation}

>>>>

::: {#fig-overview layout="[[60,-40], [70,-30]]"}
![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}

![Interactive Visualisation](images/README-TrellisOutput.png){#fig-visualisation}
